%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
\definecolor{darkblue}{rgb}{0,0,0.7}

\newcommand{\bluebold}[1]{\textcolor{darkblue}{\textbf{#1}}}
%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Jia Lin Hau} \\[7.5pt]
\href{https://github.com/monkiedein}{\raisebox{-0.05\height}\faGithub\ monkiedein} \ $|$ \ 
\href{https://linkedin.com/in/jialin-hau}{\raisebox{-0.05\height}\faLinkedin\ jialin-hau} \ $|$ \ 
\href{https://monkiedein.github.io/CV/}{\raisebox{-0.05\height}\faGlobe \ website} \ $|$ \ 
\href{mailto:jialin.hau@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ jialin.hau@gmail.com} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% Research Interest
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Research Interest}
Risk-averse reinforcement learning and decision making, deep reinforcement learning, machine learning, risk analysis, actuarial science, Bayesian method.
%EDUCATION
\section{Education}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{M.S / Ph.D. in Computer Science, University of New Hampshire} & \hfill Jan 2019 - present \\[3.75pt]
{Advisor : Marek Petrik} & \hfill GPA: 4.00 \\
\multicolumn{2}{@{}X@{}}{}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{B.S. in Applied Mathematics, University of New Hampshire} & \hfill Sep 2015 - Sep 2018 \\[3.75pt]
{Advisor : Linyuan Li} & \hfill GPA: 3.89 \\
\multicolumn{2}{@{}X@{}}{}
\end{tabularx}

%Projects
\section{Publications}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Refereed Conference Publications} &  \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{itemize}
    \item  On Dynamic Programming Decompositions of Static Risk Measures in Markov Decision Processes. \bluebold{Jia Lin Hau}, Erick Delage, Marek Petrik, Mohammad Ghavamzadeh. Conference on Neural Information Processing Systems (NeurIPS), 2023.
    \item Entropic Risk Optimization in Discounted MDPs. \bluebold{Jia Lin Hau}, Marek Petrik, Mohammad Ghavamzadeh. International Conference on Artificial Intelligence and Statistics (AISTATS), 2023.
\end{itemize}
}  
\\
\textbf{Peer Reviewed Symposia} &  \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{itemize}
    \item  Talha Siddique, \bluebold{Jia Lin Hau}, Shadi Atallah, Marek Petrik, Robust Pest Management Using Reinforcement Learning, The Multi-disciplinary Conference on Reinforcement Learning and Decision Making (RLDM), 2019
\end{itemize}
}  
\\
\textbf{Paper In Progress} &  \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{itemize}
    \item  \bluebold{Jia Lin Hau}, Marek Petrik, Erick Delage, Mohammad Ghavamzadeh, Rasr: Risk-averse soft-robust mdps with evar and entropic risk. arXiv preprint: 2209.04067, 2019.
\end{itemize}
}  
\end{tabularx}
\section{Employment}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{UNH Computer Science Department - Research Assistant} & \hfill Jun 2020 - present \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Research interest: Reinforcement learning, risk-averse optimization, machine learning, Bayesian method.}  \\
\end{tabularx}
 
 \begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{UNH Computer Science Department - Teaching Assistant} & \hfill Jan 2019 - present \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Machine Learning (CS 750/850), Computer networks (CS 725), Assembly Language and Machine Organization (CS 520), Scientific Programming in Python and C (CS 410).}  \\
\end{tabularx}

 \begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Boston Road Runner – Data Analyst} & \hfill Sep 2018 - Dec 2018\\
\multicolumn{2}{@{}X@{}}{
\begin{itemize}
    \item[-] Preprocessed (handle missing values, duplicates, and apply consistent formatting) data of participants and sponsors.
    \item[-] Developed auto-regression time series models in R to predict future trends in the number of participants for upcoming races.
    \item[-] Designed 3NF database schema using ERD and relation schema to reduce anomalies and improve data quality and integrity.
    \item[-] Created data visualizations using Tableau, which allow peers and sponsors easily interpret and understand data insights.
\end{itemize}
}  \\
\end{tabularx}
 \begin{tabularx}{\linewidth}{ @{} X@{} }
\textbf{Idea Math - Junior Instructor/ Summer Camp Resident Assistant}  \hfill Jun 2018 - Aug 2019
\end{tabularx}
 \begin{tabularx}{\linewidth}{ @{} X@{} }
\textbf{UNH International Student Organization (ISO) - Vice President}  \hfill Aug 2017 - Jun 2018
\end{tabularx}
\begin{tabularx}{\linewidth}{ @{} X@{} }
\textbf{UNH Mathematics Center - Mathematics Center Tutor}  \hfill Sep 2017 - Jun 2018
\end{tabularx}
\begin{tabularx}{\linewidth}{ @{} X@{} }
\textbf{UNH Residential Life - Resident Assistant}  \hfill Aug 2016 - Aug 2017
\end{tabularx}

\section{Other Projects}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Research Projects} &  \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{itemize}
    \item  \textbf{Risk Averse Distributional Deep Q Network}. Developed a novel methods to optimize risk averse objective for continuous domain (Atari Gym). 
    \item  \textbf{Multi-Layered chemical diffusion 3D simulation}. Implemented a complex 3D chemical simulation in Julia with GLMakie to visualize and identify the success rate of the chemical reaction. Utilize observable variables and broadcast function to speed up the continuous collision detection (CCD) by more than 10,000 times. 
\end{itemize}
}
\end{tabularx}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Software Development} &  \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{itemize}
    \item  \textbf{EMOAI} Emotion recognition application to avoid depression – \bluebold{Developer and Use Case Finder}. 
    \begin{itemize}
        \item Spearheaded Deep Learning (CNN) emotion recognition project with pre-trained models to accurately classify users’ facial expressions.
        \item Proposed groundbreaking application of the use of facial and emotion recognition technology to identify and prevent depression.
        \item Implemented active learning by allowing users to verify/update labels of their own emotion which enable personalized classification.
    \end{itemize}
    \item  \textbf{CRACC} A social apps that connect people to play sports together – \bluebold{Data / Android Developer}. \begin{itemize}
        \item Collected data from various sources (API, Kaggle, BLS), analyzed and created data visualizations with Python.
        \item Communicated effectively with the IOS team to ensure consistent UI (XML) and functionality (Java) using Android Studio.
        \item Integrated with Firebase for users’ data, and developed features that query weathers and navigation data based on users’ location.

    \end{itemize}
\end{itemize}
}
\end{tabularx}
%----------------------------------------------------------------------------------------
%	Achievements
%----------------------------------------------------------------------------------------
\section{Achievements}
\begin{tabularx}{\linewidth}{@{} X@{}}	
Passed Actuarial Science Exam P: Probability \hfill 2018 \\

Bloomberg Market Concepts (BMC) Completion \hfill 2018 \\ 

Member of Pi Mu Epsilon of National Honorary Mathematics Society \hfill  2017 \\
\end{tabularx}


%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Language &  \normalsize{Python, R, Julia, C/C++, SQL, MATLAB, HTML, CSS, JavaScript, XML, Java}\\
Tools  &  \normalsize{GLMakie, OpenGL, PyTorch, Numpy, Scikit-learn, Caret, Git, Excel, ERDPlus, Tableau}\\  
\end{tabularx}

\section{Relevant Coursework}
Reinforcement Learning, Bandit Algorithms, Mathematical Optimization, Algorithms, Computer Graphics, Assembly Language, System Programming, Formal Specification, Database System, Machine Learning, Forecasting Analysis, Numerical Methods, Linear Algebra, Differential Equation, Multi-Dimensional Calculus, Econometrics, Probability Theory, Statistical Inference, Financial Mathematics.

\section{Other}
\begin{tabularx}{\linewidth}{@{} X@{}}	

Certified NAUI Open Water Scuba Diver \hfill  2019 \\
Manchester City Marathon by SNHU (1st in co-ed relay) \hfill 2016 \\
Seacoast Half Marathon in Portsmouth (4th in division) \hfill 2015 \\
Certified PADI Advanced Open Water Scuba Diver \hfill  2013 \\

\end{tabularx}

\section{References}
\begin{tabularx}{\linewidth}{@{} l X@{}}	
Master / PhD advisor & Dr. Marek Petrik \hfill \href{mailto:mpetrik@cs.unh.edu}{\raisebox{-0.05\height}\faEnvelope \ mpetrik@cs.unh.edu}\\
External Collaborators & Dr. Mohammad Ghavamzadeh \hfill \href{mailto:mohammad.ghavamzadeh51@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ mohammad.ghavamzadeh51@gmail.com}\\
& Dr. Erick Delage \hfill \href{mailto:erick.delage@hec.ca}{\raisebox{-0.05\height}\faEnvelope \ erick.delage@hec.ca}\\
\end{tabularx}

\vfill
\center{\footnotesize Last updated: \today}

\end{document}

